\section{Background}
As the ARPANET grew throughout the 1970s, researchers started designing ways of 
sending messages to other users on remote hosts, using already standardized 
protocols such as FTP.  By 1979, there were already a myriad of incompatible 
standards, and researchers began to devise a unified standard for transferring 
mail (RFC 808).  In 1981, the Simple Mail Transfer protocol was first proposed 
in RFC 788, and later standardized in RFC 821. However, these early versions of 
SMTP did not include any support for encryption\cite{821}. It wasn't until 1995 that 
Extended SMTP (ESMTP) was standardized, which allowed for arbitrary extensions 
to the base SMTP protocol, including the support of TLS for SMTP (RFC 2487).  
Even with the addition of TLS support, SMTP servers are still not allowed to 
require encryption so that they can be backward-compatible\cite{2487}.

Today, the basic process of sending an email is the following: the sending 
client submits a message to a Mail Submission Agent (MSA), which sends the
message to a Mail Transfer Agent (MTA).  The MTA issues a DNS query to get the 
Mail Exchange (MX) records of the destination address, and sends the message to 
this server.  From there, the message is relayed (possibly using multiple MX 
record queries and forwards) to a Mail Delivery Agent (MDA).  Finally, the MDA 
delivers the message to the destination client.  It is important to note that 
both submission and delivery (Sender to MSA and MDA to Recipient) may use a 
number of different protocols, including HTTP and SMTP (on port 587) for 
submission and POP3 and IMAP for delivery.  However, the transfer from MTA to 
MX server is always done using SMTP on port 25.
