\section{Future Work}
Due to the time constraints of this project only a small sample of a few million 
domains, a larger sample of the entire internet, especially if ranked by region 
could provide good insight into that state of secure email communication on an 
country by country basis.

A follow up study collecting the same data would allow us to see how the 
adoption of TLS for SMTP is changing.

In addition to TLS, SMTP can also make use of Sender Policy Framework (SPF) 
records for authentication of email origin, and DomainKeys Identified Mail 
(DKIM) to verify message integrity. Our study could benefit further by checking 
for the usage of SPF and DKIM use coverage.  

Determine reason for Microsoft not supporting TLS. In our preliminary 
investigation, it was unclear why they would not even support the option for 
other services to send with TLS. Ideally, we would like to get in touch of 
the hotmail team to see if we can get an answer to this question directly.

Explore alternatives to SMTP for email communication. An ideal mail protocol 
would provide end-to-end email encryption. Not only would such a protocol 
provide stronger data security and integrity, but it could also have the 
potential for alleviating spam. 

Many online services send automated emails that may contain sensitive 
information such as clear text passwords, password reset links, order 
information, etc, which may not be sent via the same route as non-automated 
email from that domain. An analysis of automated email headers from popular 
providers would give us insight into this issue.
