\documentclass[11pt, twocolumn]{article}
\usepackage{graphicx}
\usepackage{url}
\usepackage{listings}
\setlength{\columnsep}{0.3in}
\usepackage[margin=1in]{geometry}
\linespread{1.05}

\author{Ian Foster, Jon Larson, and Max Masich}
\title{A Study of SMTP [in]Security}
\date{}

\begin{document}
\maketitle

\begin{abstract}
The Simple Mail Transfer Protocol (SMTP) and related Extended SMTP (ESMTP) are 
the primary means of delivering email messages between servers over the internet 
today.  Internet traffic can easily be collected by third-parties, yet 
encryption of SMTP messages is not universal, and in fact cannot be required by 
a Mail Exchange (MX) server.  This means that it is possible for an inter-domain 
email to be transferred and/or stored as plain-text at at least one point on its 
path across the internet.  This paper provides an analysis of current email 
providers and their support for TLS encryption over SMTP.  We show that while a 
majority of SMTP servers do provide support for TLS, almost half of all email 
users use a provider that does not support TLS encryption according to the 
standard ESMTP protocol.  We further show that of those email providers that 
ostensibly support TLS, a number of them are configured such that their true 
security is suspect (e.g. invalid certificates, weak ciphers).  Our aim is to 
raise awareness of the vulnerabilities present in the current SMTP environment
on the internet.
\end{abstract}

\input{intro}
\input{background}

\section{Related Works}
From what we could find, there has been no similar work done specifically 
studying the state of security of the SMTP ecosystem. 

On the other hand, there have been studies of a similar vein on the state HTTPS. 
One in particular that we drew inspiration from was \cite{https} in our analysis 
of SMTP TLS certificate validity. 

\input{methodology}
\input{results}
\input{future}
\input{conclusion}

\begin{thebibliography}{1}
    \bibitem{alexa}
        Alexa Top 1,000,000 Sites

        \url{http://www.alexa.com/topsites/global}
    \bibitem{https}
        Analysis of the HTTPS Certiﬁcate Ecosystem

        \url{http://web.eecs.umich.edu/~mibailey/publications/imc13\_https\_final.pdf}
    \bibitem{adobe}
        Adobe Email Leak

        \url{http://www.theguardian.com/technology/2013/nov/07/adobe-password-leak-can-check}
    \bibitem{gawker}
        Gawker Email Leak

        \url{http://www.slate.com/articles/technology/technology/2010/12/was\_your\_gawker\_password\_hacked.html}
    \bibitem{sony}
        Sony Email Leak
    \bibitem{821}
        RFC 821

        \url{http://tools.ietf.org/html/rfc821}
    \bibitem{2487}
        RFC 2487

        \url{http://tools.ietf.org/html/rfc2487}
    \bibitem{code}
        Project Code

        \url{https://github.com/lanrat/smtp-scanner}
    \bibitem{mail}
        Mail Parameters

        \url{http://www.iana.org/assignments/mail-parameters/mail-parameters.xhtml}
\end{thebibliography}

\end{document}
